---
title: "Data 605 Assignment13"
author: "Raghu"
date: "November 21, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Use integration by substitution to solve the integral below.

$$\int 4e^{-7x} dx$$ 

Let u = -7x

$$\frac {du} {dx} = -7$$
$$\frac {du} {-7} =dx$$
$$\frac {-4} {7} \int e^u du$$
$$\frac {-4} {7} e^u $$

$$\frac {-4} {7} e^{-7x} + C $$

### 2. Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of $$\frac {dN} {dt} =  \frac {- 3150} {t^4} - 220 $$  bacteria per cubic centimeter per day, where t is the number of days since treatment began. Find a function N(t) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter.


$$\frac {dN} {dt} =  \frac {- 3150} {t^4} - 220 $$
$$N =  3150 \frac  {t^-3} {-3} - 220t + C $$
t=1
N=6530

$$6530 =  -1050 (1^{-3}) - 220(1) + C $$
$$6530 +  1270 = C $$
$$7800 = C $$

$$N =   \frac  {-3150}{3t^3}  - 220t + 7800 $$
$$N =   \frac  {-1050}{t^3}  - 220t + 7800 $$

### 3. Find the total area of the red rectangles in the figure below, where the equation of the line is f(x) = 2x - 9.

$$ Area = \int_{4.5}^{8.5}  2x - 9 dx$$ 
$$ Area = \bigg[x^2 - 9x \bigg] _{4.5}^{8.5} $$

$$ Area = \bigg[8.5^2 - 9 * 8.5 \bigg]  - \bigg[4.5^2 - 9 * 4.5 \bigg] $$

```{r c3}
Area <- (8.5^2 - 9*8.5) - (4.5^2 - 9*4.5)

Area

```

### 4. Find the area of the region bounded by the graphs of the given equations.
$$ y =x^2 -2x - 2, y = x + 2 $$
$$A = (x^2 - 2*x - 2 ) $$
$$B =  x + 2$$

$$Area =A-B$$

$$ (x^2 - 2*x - 2 ) - (x +2)$$

$$ (x^2 - 2x - 2  - x - 2)$$

$$ (x^2 - 3x - 4 )$$
$$ (x^2 - 4x +x - 4 )$$
$$ x*(x-4) + 1(x - 4 )$$

$$ x = -1 and 4 $$

$$ \int_{-1}^{4}f(x)dx = \int_{-1}^{4} (x^2 - 3x - 4 )$$
$$  = \bigg[ \frac {(x^3)}{3} - \frac{3x^2}{2} - 4x ) \bigg]_{-1}^{4}$$
$$  = \bigg[ \frac {(64)}{3} - \frac{48}{2} - 16 ) \bigg] - \bigg[ \frac {(-1)}{3} - \frac{3}{2} + 4\bigg]$$
$$  = \bigg[ \frac {64}{3} - 40 \bigg] - \bigg[ \frac {-1}{3} - \frac{3}{2} + 4\bigg]$$
```{r c4.1}
a <- 64/3 - 40 + (1/3) + (3/2) -4
a

# create functions a and b
f <- function(x) {x^2-2*x-2}
g <- function(x) {x+2}
# plot to visualize
curve(f, -6, 6)
curve(g, -6, 6, add=TRUE)
# integrate g
g_area <- integrate(g, lower = -1, upper = 4)
# integrate f
f_area <- integrate(f, lower = -1, upper = 4)
g_area$value - f_area$value

```

### 5. A beauty supply store expects to sell 110 flat irons during the next year. It costs $3.75 to store one flat iron for one year. There is a fixed cost of $8.25 for each order. Find the lot size and the number of orders per year that will minimize inventory costs.


lot size = x units/order

Annual Cost = Annual storage cost * Average no. of items carried out a year

Annual Cost = 3.75.x/2 =1.875x

$$Annual Order Cost = Cost of Order * number of orders/year  = (8.25 * 110/x)$$

$$Total inventory cost = 1.875x + (8.25 * 110/x)$$
$$y = 1.875x + (907.5/x)$$
$$y` = 1.875x + (907.5/x) = 0$$
$$ 1.875 - (907.5/x^2) = 0 $$
$$ x^2= 907.5/1.875 $$

$$ x^2= 206.25 $$


```{r c5}
A <- sqrt(206.25)
A
```
lot size =14.36/order

```{r c5.1}
ordperyear <- 110/14.36
ordperyear
```

Orders per year = 7.6



### 6. Use integration by parts to solve the integral below.

$$ Area = \int  ln(9x).x^6 dx$$ 

$$U = ln(9x)$$
$$dU = \frac {1} {x} dx $$
$$dV = x^6dx$$
$$V = \frac {1} {7} x^7$$
$$UdV = UV - \int VdU $$

$$ ln(9x)\frac {1} {7} x^7 -  \int \frac {1} {7} x^7 \frac {1} {x} dx$$

$$ \frac {1} {7} ln(9x) x^7 -   \frac {1} {7} \int x^6  dx$$
$$ \frac {1} {7}x^7[ln(9x)] - \frac {1} {7}    ] dx$$


### 7. Determine whether f(x) is a probability density function on the interval [ 1, e^6 ] . If not, determine the value of the definite integral.


$$ f(x) = \frac {1} {6x} $$
$$ F(x) = \int_{1}^{e^6}  f(x) dx = 1 $$
substituting f(x)

$$ F(x) = \int_{1}^{e^6}  \frac {1} {6x} dx  $$
$$ F(x) = \frac {1} {6} \int_{1}^{e^6}  \frac {1} {x} dx  $$

$$ F(x) = \frac {1} {6} \bigg[ln(x) \bigg]_{1}^{e^6} $$

$$ F(x) = \frac {1} {6} \bigg[ln(e^6) - ln(1) \bigg] $$
$$ F(x) = \frac {1} {6} \bigg[6 - 0 \bigg] = 1 $$

