---
title: "DATA 605 Assignment1"
author: "Raghu"
date: "August 26, 2017"
output: html_document
---



## PROBLEM SET 1


### (1) Calculate the dot product u.v where u = [0.5;0.5] and v = [3;−4] 

```{r q1.1, include=TRUE}

u <- c(0.5,0.5)
v <- c(3,-4)

dot_prod <- u %*% v

dot_prod

```

### (2) What are the lengths of u and v? Please note that the mathematical notion of the length of a vector is not the same as a computer science deﬁnition.

```{r q1.2, include=TRUE}

len_u <- sqrt(sum(u*u))
len_v <- sqrt(sum(v*v))
len_u
len_v
```

### (3) What is the linear combination: 3u−2v? 

```{r q1.3, include=TRUE}

lin_cmb <- (3*u) - (2*v)
lin_cmb

```

### (4) What is the angle between u and v

```{r q1.4, include=TRUE}

angle <- acos(dot_prod/(len_u * len_v))
angle


```


## PROBLEM SET 2

### Please write a function in R that will take two variables (matrix A & constraint vector b) and solve using elimination

```{r q2, include=TRUE}

# Function to solve 3X3 matrix system equation
mysolve <- function(a,b){
  
  # add on the constraint vector as column to matrix
  se <- cbind(a, b)
  
  # gauss transform: for row 2
  se[2,] <- -1 * se[2,1]/se[1,1] * se[1,] + se[2,]
  
  # gauss transform: for row 3, col 1
  se[3,] <- -1 * se[3,1]/se[1,1] * se[1,] + se[3,]
  
  # gauss transform: for row 3, col 2
  se[3,] <- -1 * se[3,2]/se[2,2] * se[2,] + se[3,]
  
  # substitution 
  z <- se[3,4] / se[3,3]
  
  y <- (se[2,4] - se[2,3] * z) / se[2,2]
  
  x <- (se[1,4] - se[1,3] * z - se[1,2] * y) / se[1,1]
  
  
  result <- as.vector(round(c(x,y,z), digits=2))
  
  return(result)
}


A <- t(matrix(c(1,1,3,2,-1,5,-1,-2,4), ncol=3))

cons <- c(1,2,6)

mysolve(A,cons)

```
