---
title: "Data 605 Assignment7"
author: "Raghu"
date: "October 14, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Problem1. 
Let X1, X2, . . . , Xn be n mutually independent random variables, each of
which is uniformly distributed on the integers from 1 to k. Let Y denote the
minimum of the Xi's. Find the distribution of Y .


ANS:  

For $$ 1 \leq  j \leq k, m(j) =   (k-j+1)^n - (k - j)^n  /  k^n  $$
    
     
Since $Y$ is the minimum value of $Xi$ over all of the $Xi'$s, then in order to find the distribution function $m(j) = P(Y = j)$, we will need to count the number of ways that we can assign $X1,X2......Xn$ to values between j and k with at least one $Xi$ being assigned to j and divide by the total number of possible ways to assign $X1,X2......Xn$ to values between 1 and k.

  
First, suppose that each $Xi$ has k possibilities: 1, 2,....k. Then, the total possible number of assignments for the entire collection of random variables $X1,X2......Xn$ is $k^n$. This will form the denominator for probability distribution function.

  
Now, the number of ways of getting $Y = 1$ is  $$ k^n -(k-1)^n $$

since $$k^n$$ represents the total number of options and $ (k-1)^n $ represents all of the options where none of the $Xi'$s are equal to 1.

  
If $Y = 2$, then there are $$ k^n -(k-2)^n - [ k^n -(k-1)^n ] $$
different options for the collection of $ Xi $ 's, where the $$k^n$$ represents the total number of options (with no restrictions), $$(k-2)^n$$ represents the number of ways that we could assign $X1,X2......Xn$ with all of their values being greater than 2, and, as we showed above,  $$[k^n -(k-1)^n]$$  represents the number of ways that we could assign $X1,X2......Xn$ and have at least one of them equal 1 (i.e. Y = 1). We can simplify above equation to get $$ (k - 1)^n - (k - 2)^n $$


In general, if Y = j then there are $$ ( k - j + 1)^n -(k-j)^n $$ ways  to assign $X1,X2......Xn$ so that minimumvalue is j.  




###Problem 2. 

Your organization owns a copier (future lawyers, etc.) or MRI (future doctors). This machine has a manufacturer's expected lifetime of 10 years. This means that we expect one failure every ten years. (Include the probability statements and R Code for each part.).



a. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a geometric. (Hint: the probability is equivalent to not failing during the first 8 years..)

E(X)=ns=10
Probability that machine fail once every 10 years

s is the probability that the machine fail 

q is the probability that the machine does not fail

```{r P1.a, include=TRUE}
s=1/10
s
q=1-s
q
#ns=10
n=10/s
n
#v(x)=nsq
n*s*q
# Probability that machine will fail after 8 years
#using R function pgeom
p <- pgeom(8, s, lower.tail = F)
p
#probability will copier will fail
p = 1 -p
p
#expected value:mean 
#s is probabity of copier failure
m <- round(1/s,2)
m
#standard deviation
sd <- round(sqrt((1-s)/(s^2)),2)
sd

```

$$ P(X>=9) = P( (X - EX(X))/\sqrt{(V(X)})$$



b. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as an exponential.

Using Exponential Distribution $p(n) = e^{{-\lambda}x}$, probability that copier will be working or fail after $8$ years is,

Expected value ns =10
Standard deviation = $\sqrt{(V(X)})$

```{r Pb, include=TRUE}
#number of trials
i = 8
#failure rate of copier
s = 1/10
#copier working
f = 1 - s

#using R function pexp
p <- pexp(8, s, lower.tail = F)
p
#probability will copier will fail
p = 1 -p
p
#expected value: mean 
#s is probabity of copier failure, lambda
m <- round(1/s,2)
m
#standard deviation
#in expontential distribution standard deviation = mean
sd <- m
sd
```




c. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8 years)


P(X = X) =  $$ {{8}\choose{x}} (0.10)^x (0.90)^{8-x} $$


P(X = 8) =  $$ {{8}\choose{8}} (0.10)^8 (0.90)^{8-8} $$

=0.43


```{r P2, include=TRUE}

#number of trials
i = 8
#probability of failure rate of copier
s = 1/10
#copier working
d = 1 - s
#using R function pbinom
p <- pbinom(0, size=8, prob=0.1)
p
#probability will copier will fail
p = 1 -p
p
#expected value:mean 
#s is probabity of failure
#i is number of years
m <- round(i * s,2)
m
#standard deviation
#square root of mean * (1-p)
sd <- sqrt(m * d)
sd
```

d. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a Poisson.


```{r P3, include=TRUE}
#number of trials
t = 8
#mean or average failure rate of copier(success) in 8 years
k = 0
#probability of failure 
p = 1/10

#lambda = years * probability of failure
l = t * p
#using R function ppois
pp <- ppois(0, lambda = l)
pp
#probability will copier will fail
pp = 1 -pp
pp
#expected value: mean 
#s is probabity of failure(p)
#i is number of years(n)
m <- round(l,2)
m
#standard deviation
#square root of mean
sd <- sqrt(m)
sd
```

