---
title: "Data 605 Assignment3"
author: "Raghu"
date: "September 14, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Problem set 1
### (1) What is the rank of the matrix A?

```{r P1.1, include=TRUE}

A1 <- matrix(c(1,2,3,4,-1,0,1,3,0,1,-2,1,5,4,-2,-3), nrow = 4, byrow = T)

A1

#After the row reduced echelon matrix
A<- matrix(c(1,2,3,4,0,2,4,7,0,0,-4,-5/2,0,0,0,9/8), nrow= 4, ncol=4, byrow= TRUE)

A

```


Ans: From the above matrix, its known that its dimension is 4x4 square matrix and lineary independent, therefore it rank is 4

(2) Given an mxn matrix where m > n, what can be the maximum rank? The minimum rank, assuming that the matrix is non-zero?

Ans:if m is greater than n, then the maximum rank of the matrix is n and if m is less than n, then the maximum rank of the matrix is m.

(3) What is the rank of matrix B?
B =

```{r P1.3, include=TRUE}

B <- matrix(c(1,2,1,3,6,3,2,4,2), nrow = 3, byrow = T)

B

dim(B)

R1 <- B[1, ]
R2 <- B[2, ]
R3 <- B[3, ]

a <- R1-(1/3)%*%R2
b <- R3-(2/3)%*%R2


M <- matrix(c(a,b,R2), nrow = 3, byrow = T)

M

```

Answer: Since the rank is number of non zero row, rank is 1.

###2. Problem set 2
###Compute the eigenvalues and eigenvectors of the matrix A. You'll need to show your
###work. You'll need to write out the characteristic polynomial and show your solution.

```{r P2, include=TRUE}

B <- matrix(c(1,2,3,0,4,5,0,0,6), nrow = 3, byrow = T)

B

```



$$
pB(\lambda) = det(B-(\lambda I3))
$$
$$ =
\begin{pmatrix}
1-\lambda & 2 & 3\\
0 & 4-\lambda & 5\\
0 & 0 & 6-\lambda \\
\end{pmatrix}
$$
$$ 
= (1-\lambda)[(4-\lambda)(6-\lambda)-(0)(5)] - 2[0] + 3[0]
$$
$$
= (1-\lambda)[(4-\lambda)(6-\lambda)]
$$

$$
\lambda = 1, 4 and 6
$$
$$
Substituting \lambda = 1,  Eigen vectors are = 
\Bigg[\begin{pmatrix}
&1\\
&0\\
&0\\
\end{pmatrix}
\Bigg]
$$
$$
Substituting \lambda = 4,  Eigen vectors are = 
\Bigg[\begin{pmatrix}
&1.6\\
&2.5\\
&1\\
\end{pmatrix}
\Bigg]
$$

$$
Substituting \lambda = 6,  Eigen vectors are = 
\Bigg[\begin{pmatrix}
&0.6\\
&1\\
&0\\
\end{pmatrix}
\Bigg]
$$

```{r P2.2, include=TRUE}

eigen(B, only.values = FALSE, EISPACK = TRUE)

```

