---
title: "Data 605 Assignment12"
author: "Raghu"
date: "November 17, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The attached who.csv dataset contains real-world data from 2008. The variables included follow.

Country: name of the country
LifeExp: average life expectancy for the country in years
InfantSurvival: proportion of those surviving to one year or more
Under5Survival: proportion of those surviving to five years or more
TBFree: proportion of the population without TB.
PropMD: proportion of the population who are MDs
PropRN: proportion of the population who are RNs
PersExp: mean personal expenditures on healthcare in US dollars at average exchange rate
GovtExp: mean government expenditures per capita on healthcare, US dollars at average exchange rate
TotExp: sum of personal and government expenditures.

### 1. Provide a scatterplot of LifeExp~TotExp, and run simple linear regression. Do not transform the variables. Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss whether the assumptions of simple linear regression met.

###Read csv file
```{r rwd}

library(knitr)
url <- "C:/cuny/Fall_2017/DATA-605/Assignment12/who.csv"
rwd  <- read.csv(file = url, header = T, stringsAsFactors = F)

summary(rwd)


kable(head(rwd))

#scatter plot
plot(rwd$LifeExp, rwd$TotExp, main="Scatterplot", 
    xlab="Life Expectancy ", ylab="Total Expenidutres ", pch=19) 



#simple linear regression
lm_rwd <- lm(rwd$LifeExp ~ rwd$TotExp)
abline(lm_rwd, col = "red")

#residuals
hist(resid(lm_rwd), main = "Histogram of Residuals", xlab = "residuals")

#summary
summary(lm_rwd)

```



### 2. Raise life expectancy to the 4.6 power (i.e., LifeExp^4.6). Raise total expenditures to the 0.06 power (nearly a log transform, TotExp^.06). Plot LifeExp^4.6 as a function of TotExp^.06, and r re-run the simple regression model using the transformed variables. Provide and interpret the F statistics, R^2, standard error, and p-values. Which model is "better?"



```{r rwd2}

#simple linear regression
x <- rwd$LifeExp^4.6
y <- rwd$TotExp^0.06
lm_rwd2 <- lm(x ~ y)

#scatter plot
plot(x, y, main="Scatterplot 2", 
    xlab="Life Expectancy ", ylab="Total Expenidutres ", pch=19) 

abline(lm_rwd2, col = "red")

#residuals
hist(resid(lm_rwd2), main = "Histogram of Residuals", xlab = "residuals")

#summary
summary(lm_rwd2)

plot(fitted(lm_rwd), resid(lm_rwd))
plot(fitted(lm_rwd2), resid(lm_rwd2))

```

     Model2 is highly different and better compared to Model1. Adjusted Rsquare is 72% whereas Model1 is only 25%. 72% can be explained by model2. There seems to be a good correlation. p-value is less in Model2 compared to Model1. F-stat is 507 in model2 whereas only 65 in Model1. Residual standard error is high in Model2 and normally distributed in Model2. 

### 3. Using the results from 3, forecast life expectancy when TotExp^.06 =1.5. 
###  Then forecast life expectancy when TotExp^.06=2.5.

$$y= -736527910  + 620060216 x$$


$$life expectancy = y^(1/4.6)$$

```{r rwd3}


le <- function(fc)
{   y <- -736527910 + 620060216 * (fc)
    y <- y^(1/4.6)
    print(y)
}
#Life expectancy when TotExp^.06 =1.5
le(1.5)
#Life expectancy when TotExp^.06 =2.5
le(2.5)

```



### 4. Build the following multiple regression model and interpret the F Statistics, R^2, standard error, and p-values. How good is the model?
### LifeExp = b0+b1 x PropMd + b2 x TotExp +b3 x PropMD x TotExp

```{r rwd4}
lm_fit3 <- lm(rwd$LifeExp ~ rwd$PropMD + rwd$TotExp + rwd$PropMD*rwd$TotExp)
summary(lm_fit3)
hist(resid(lm_fit3), main = "Histogram of Residuals", xlab = "residuals")
plot(fitted(lm_fit3), resid(lm_fit3))

```


      
      p-value is less than .05. model is statistically significant. F-statistic is 34.49 by adding 3 variables. Based on Rsquare only 35% of the variability can be explained by 3 variables. Correlation is moderate in this case. Residuals is right skewed. So, linear model is not valid.	  


### 5. Forecast LifeExp when PropMD=.03 and TotExp = 14. Does this forecast seem realistic? Why or why not?


$$LifeExp = 6.277 * 10^1 + 1.497*10^3 * PropMD + 7.233* 10^-5 TotExp-6.026*10^-3 *PropMD*TotExp$$


```{r rwd5}
LE <- ( (6.277*10^1) + (1.497*10^3)*.03 + (7.233*10^(-5))*14 - ((6.026*10^(-3))*0.03*14) ) 
LE
```

    ###The forecast age 107.6 is an outlier and seems to be unrealistic. The expenditure is also low. 