---
title: "Data 605 Assignment5"
author: "Raghu"
date: "September 29, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Choose independently two numbers B and C at random from the interval [0, 1] with uniform density. Prove that B and C are proper probability distributions.
Note that the point (B,C) is then chosen at random in the unit square.

Find the probability that

##(a) B + C < 1/2.


$$ P\Bigg(B+C < 1/2\Bigg) $$
$$ = P\Bigg( X + Y < 1/2\Bigg) $$

$$ = P\Bigg( 0 < X < 1/2 , 0 <  Y < 1/2 - x \Bigg) $$

$$=\int_{0}^{1/2}\int_{0}^{1/2-x} f(x,y) dxdy $$

$$=\int_{0}^{1/2}\int_{0}^{1/2-x}  1.dydx $$
$$=\int_{0}^{1/2}[1/2-x]  dx $$

$$ =\Bigg[ 1/2x - x^2/2 \Bigg]_{0}^{1/2}   $$
$$ =1/4 - 1/8 $$

$$ = 1/8 $$



## (b) BC < 1/2.

$$ P\Bigg( B.C < 1/2\Bigg) = \int_{0}^{1/2} f(z) dz  $$


```{r P1.1, include=TRUE}

f <- function(x) {x}
res = integrate(f, lower = 0, upper = 0.5)
res

```




## (c) |B -C| < 1/2


P (|B - C| < 1/2  given that 0 < x +y < 1)

$$ P (|X - Y| < 1/2   given that 0 < x +y < 1) $$ 
$$ = P\Bigg( -1/2 < X - Y  < 1/2 ; 0 <  X  <  1 - Y \Bigg) $$
$$ = P\Bigg( 0 < X   <  1/2-Y ; 0 <  Y  <  1/2  \Bigg) $$
$$=\int_{0}^{1/2}\int_{0}^{1/2-y}  f(x,y)dxdy $$
$$=\int_{0}^{1/2}\int_{0}^{1/2-y}  1.dxdy $$

$$=\int_{0}^{1/2}[x]_{0}^{1/2-y}  dy $$

$$=[Y/2 - Y^2/2]_{0}^{1/2} $$
$$ = 1/4 - 1/8 $$
$$=0.125$$

##(d) max{B,C} < 1/2.

$$ =  P\Bigg( max(B,C )< 1/2\Bigg) $$

$$ =  P\Bigg( B <= 1/2 ,C <=1/2 \Bigg) $$
$$ =  P\Bigg( B <= 1/2  \Bigg) P\Bigg( C <=1/2 \Bigg) $$

$$ = 1/2 * 1/2 $$
$$ = 1/4$$


## (e) min{B,C} < 1/2.

$$ =  P\Bigg( min(B,C )<= 1/2\Bigg) $$
$$ =  1 - P\Bigg( min(B,C ) > 1/2\Bigg) $$
$$ =  1 - P\Bigg( B > 1/2,C >1/2 \Bigg) $$
$$ =  1 - P\Bigg( B > 1/2\Bigg) P\Bigg( C > 1/2\Bigg) $$
$$ =  1 - \Bigg[ 1 - P\Bigg( B > 1/2\Bigg)\Bigg] \Bigg[1 -  P\Bigg( C > 1/2\Bigg)\Bigg] $$
$$ =  1 - \Bigg[ 1 -  1/2\Bigg] \Bigg[1 -    1/2\Bigg] $$
$$ =  1 - \Bigg[ 1/2\Bigg] \Bigg[1/2\Bigg] $$


$$ =  1 - 1/4 $$


$$ =  3/4 $$
