---
title: "Data 605 Assignment10"
author: "Raghu"
date: "November 2, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Problem1
Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars.
A guard agrees to make a series of bets with him. If Smith bets A dollars,
he wins A dollars with probability .4 and loses A dollars with probability .6.
Find the probability that he wins 8 dollars before losing all of his money if

(a) he bets 1 dollar each time (timid strategy).

The Markov chain (Xn, n = 0, 1, . . .) representing the evolution of
Smith's money

Let $\varphi(i)$ be the probability that the chain reaches state 8 before reaching state 0, starting from state i. In other words, if $S_j$ is the first $n \geq 0$ such that 
$X_n = j$,


$$\varphi(i) = P_i(S_8 < S_0) = P(S_8 < S_0|X_0 = i)$$

Using first-step analysis (viz. the Markov property at time n = 1), we have

$$\varphi(i) = 0.4\varphi(i + 1) + 0.6\varphi(i - 1),   i = 1, 2, 3, 4, 5, 6, 7$$

$$\varphi(0) = 0$$

$$\varphi(8) = 1$$
```{r P1.a, include=TRUE}

q <- 0.6
p <- 0.4
m <- 8
qp = q/p
for (s in 1:8) {
P = (1 - qp^s)/(1-qp^m)
print(paste0("s: " ,s," P:  ", P))
#print(P)
}

```



(b) he bets, each time, as much as possible but not more than necessary to
bring his fortune up to 8 dollars (bold strategy).


ANS: Since the prisoner bets A dollars and will lose or gain A dollars, and he bets his entire money each time until 8$. he must win each time or lose. If he  wins sequence is: 1,2,4,8. He starts with 1 dollar and must win 3 bets in a row at p=0.4 
p=0.4

```{r P1.b, include=TRUE}

0.4^3

```

(c) Which strategy gives Smith the better chance of getting out of jail?


Bold strategy gives Smith a better chance to get out of jail.